### 2016-04-15 lineups.Rnw
teensy bit of a comment

\begin{table}[h]
\caption{\label{tab:models}Parameters and estimates of models $M_1$ and $M_2$.}
\centering
\scalebox{0.8}{
\begin{tabular}{lccrr}
Effect name & Symbol & Corresponding Statistic & $M_1$ Estimate & $M_2$ Estimate\\
\hline
\hline
Rate 1 (wave 1 $\rightarrow$ 2) & $\alpha_1$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2 $ & \Sexpr{round(lineup1$null_mod_ests[1], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[1],3)}\\
Rate 2 (wave 2 $\rightarrow$ 3) & $\alpha_2$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2 $ & \Sexpr{round(lineup1$null_mod_ests[2], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[2],3)}\\
Outdegree & $\beta_1$ & $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ & \Sexpr{round(lineup1$null_mod_ests[3], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[3],3)}\\
Reciprocity & $\beta_2$ & $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ & \Sexpr{round(lineup1$null_mod_ests[4], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[4],3)}\\
Jumping Transitive Triplets & $\beta_3$ & $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$ & -- & \Sexpr{round(lineup1$alt_mod_estimates[5],3)}
\end{tabular}}
\end{table}

\begin{figure}
<<hist-estimates, echo=FALSE>>=
# nulls <- read.csv("Data/distribution_null_model.csv")
# names(nulls)[-1] <- c("alpha1", "alpha2", "beta1", "beta2")
# nulls$Sim <- 1:nrow(nulls)
# nulls$Model <- "M1"
# 
# alt <- read.csv("Data/distribution_jumpTT_model.csv")
# names(alt)[-1] <- c("alpha1", "alpha2", "beta1", "beta2", "beta3")
# alt$Sim <- 1:nrow(alt)
# alt$Model <- "M2"
# 
# alt2 <- gather(alt, parameter, estimate, 2:6)
# null2 <- gather(nulls, parameter, estimate, 2:5)
# 
# simu <- rbind(alt2[,-1], null2[,-1])
# write.csv(simu, "Data/simulation-1000-M1-M2.csv", row.names=FALSE)

@@

After estimating the parameters in each of these models, we simulate from them to obtain realizations of each of the models. The objective function for each actor in each model is given below. 
\hh{It might be better to re-phrase the two functions below from `null' and `data' to model $M_1$ and model $M_2$, where $M_1$ is nested within model $M_2$. Both $M_1$ and $M_2$ are based on the data - so the distinction between null and data might add a bit of confusion, when we flip the models around in the next step.  }
  \begin{align*}
  f^{null}_{i}(x) & = \hat{\beta}_1^{null}s_{i1}(x) +  \hat{\beta}_2^{null}s_{i2}(x) \\
  f^{alt}_{i}(x) & = \hat{\beta}_1^{alt}s_{i1}(x) +  \hat{\beta}_2^{alt}s_{i2}(x) + \hat{\beta}_3^{data}s_{i3}(x) 
  \end{align*}
The rate parameters, $\alpha_1$ and $\alpha_2$ represent how many opportunities for change each actor gets when moving from wave 1 to 2 and from wave 2 to 3, respectively.

>>>>

\begin{table}[h]
\caption{\label{tab:models}Parameters and estimates of models $M_1$ and $M_2$. \hh{Estimates stem from one of the simulations. XXX We probably should change that to the average of the 1000 simulations, and then simulate the lineups from those, like you suggested. }}
\centering
\scalebox{0.8}{
\begin{tabular}{lccrr}
Effect name & Parameter & Corresponding Statistic & $M_1$ Estimate & $M_2$ Estimate\\
\hline
\hline
Rate 1 (wave 1 $\rightarrow$ 2) & $\alpha_1$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2 $ & \Sexpr{round(lineup1$null_mod_ests[1], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[1],3)}\\
Rate 2 (wave 2 $\rightarrow$ 3) & $\alpha_2$ & $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2 $ & \Sexpr{round(lineup1$null_mod_ests[2], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[2],3)}\\
Outdegree & $\beta_1$ & $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ & \Sexpr{round(lineup1$null_mod_ests[3], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[3],3)}\\
Reciprocity & $\beta_2$ & $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ & \Sexpr{round(lineup1$null_mod_ests[4], 3)} & \Sexpr{round(lineup1$alt_mod_estimates[4],3)}\\
Jumping Transitive Triplets & $\beta_3$ & $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$ & -- & \Sexpr{round(lineup1$alt_mod_estimates[5],3)}
\end{tabular}}
\end{table}

\begin{figure}
\centering
<<hist-estimates, echo=FALSE, fig.width=8, fig.height=5, out.width='.8\\linewidth'>>=
# nulls <- read.csv("Data/distribution_null_model.csv")
# names(nulls)[-1] <- c("alpha1", "alpha2", "beta1", "beta2")
# nulls$Sim <- 1:nrow(nulls)
# nulls$Model <- "M1"
# 
# alt <- read.csv("Data/distribution_jumpTT_model.csv")
# names(alt)[-1] <- c("alpha1", "alpha2", "beta1", "beta2", "beta3")
# alt$Sim <- 1:nrow(alt)
# alt$Model <- "M2"
# 
# alt2 <- gather(alt, parameter, estimate, 2:6)
# null2 <- gather(nulls, parameter, estimate, 2:5)
# 
# simu <- rbind(alt2[,-1], null2[,-1])
# write.csv(simu, "Data/simulation-1000-M1-M2.csv", row.names=FALSE)

@@

After estimating the parameters in each of these models, we simulate from them to obtain realizations of each of the models. The objective function for each actor in each model is given below. 
  \begin{align*}
  f^{M_1}_{i}(x) & = \hat{\beta}_1^{M_1}s_{i1}(x) +  \hat{\beta}_2^{M_1}s_{i2}(x) \\
  f^{M_2}_{i}(x) & = \hat{\beta}_1^{M_2}s_{i1}(x) +  \hat{\beta}_2^{M_2}s_{i2}(x) + \hat{\beta}_3^{M_2}s_{i3}(x) 
  \end{align*}
The rate parameters, $\alpha_1$ and $\alpha_2$ represent how many opportunities for change each actor gets when moving from wave 1 to 2 and from wave 2 to 3, respectively.
